Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex

All the experiments in this section were conducted on Summit. Summit is a supercomputer created by IBM for the Oak Ridge National Laboratory. 
There are approximately 4,600 nodes on Summit. 
Each node contains two IBM POWER9 processors on separate sockets with 512 GB of DDR4 memory.
Each POWER9 processor utilizes 22 IBM SIMD Multi-Cores (SMCs), although one of these SMCs on each processor is dedicated to memory transfer and is therefore not available for computation. 
For node scaling experiments, all 42 available SMCs were utilized in each node so that every node computed with 42 separate MPI processes.
Additionally, every node also supports six NVIDIA Volta V100 accelerators but these were unused by our algorithm.

@@

	We use the Hyperspectral Digital Imagery Collection Experiment (HYDICE) image of the Washington DC Mall. We will refer
	to this dataset as \hyper{}\cite{DC-HYDICE}.

	\hyper{} is formatted into a 3-way tensor representing two spatial dimensions of pixels and one dimension of spectral bands. So, a slice along
	the spectral band dimension would be the full \hyper{} image in that spectral band. For hierarchical clustering, these tensors are flattened so that the rows represent the
	$191$ spectral bands and the columns represent the $392960$ pixels.   The data set is approximately 600 MB in size.

@@

	The SIIM-ISIC Melanoma classification
	dataset, which we will refer to as \image{}\cite{SIIM-ISIC}, consists of $33126$ RGB training images equally sized at $1024 \times 1024$. Unlike with hyperspectral imaging, the resulting
	matrix used in hierarchical clustering consists of image pixels along the rows and individual images along the columns. So, the resulting sized matrix is
	$3145728 \times 33126$, which is approximately 800 GB in size.

	Given its size, \image{} requries $10$ Summit nodes to perform hierarchical clustering.

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_rank2_speedup.pdf}
\caption{Strong Scaling for Rank-2 NMF on Synthetic}
\label{fig:synrank2speedup}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_rank2_speedup.pdf}
\caption{Strong Scaling for Rank-2 NMF on \image{}}
\label{fig:rwrank2speedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_rank2_strongscaling.pdf}
\caption{Time Breakdown for Rank-2 NMF on \image{}}
\label{fig:rwrank2strongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_hierarchical_speedup.pdf}
\caption{Strong Scaling for Hierarchical Clustering on Synthetic}
\label{fig:synhierspeedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_hier_strongscaling.pdf}
\caption{Time Breakdown for Hierarchical Clustering on Synthetic}
\label{fig:synhierstrongscaling}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_hierarchical_speedup.pdf}
\caption{Strong Scaling for Hierarchical Clustering on \image{}}
\label{fig:rwhierspeedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_hier_strongscaling.pdf}
\caption{Time Breakdown for Hierarchical Clustering on \image{}}
\label{fig:rwhierstrongscaling}
\end{center}
\end{figure}

>>>>

All the experiments in this section were conducted on Summit. Summit is a supercomputer created by IBM for the Oak Ridge National Laboratory. 
There are approximately 4,600 nodes on Summit. 
Each node contains two IBM POWER9 processors on separate sockets with 512 GB of DDR4 memory.
Each POWER9 processor utilizes 22 IBM SIMD Multi-Cores (SMCs), although one of these SMCs on each processor is dedicated to memory transfer and is therefore not available for computation. 
For node scaling experimeheight=2innts, all 42 available SMCs were utilized in each node so that every node computed with 42 separate MPI processes.
Additionally, every node also supports six NVIDIA Volta V100 accelerators but these were unused by our algorithm.

@@

	We use the Hyperspectral Digital Imagery Collection Experiment (HYDICE) image of the Washington DC Mall. We will refer
	to this dataset as \hyper{}\cite{DC-HYDICE}.
	\hyper{} is formatted into a 3-way tensor representing two spatial dimensions of pixels and one dimension of spectral bands. So, a slice along
	the spectral band dimension would be the full \hyper{} image in that spectral band. For hierarchical clustering, these tensors are flattened so that the rows represent the
	$191$ spectral bands and the columns represent the $392960$ pixels.   The data set is approximately 600 MB in size.

@@

	The SIIM-ISIC Melanoma classification
	dataset, which we will refer to as \image{}\cite{SIIM-ISIC}, consists of $33126$ RGB training images equally sized at $1024 \times 1024$. Unlike with hyperspectral imaging, the resulting
	matrix used in hierarchical clustering consists of image pixels along the rows and individual images along the columns. So, the resulting sized matrix is
	$3145728 \times 33126$, which is approximately 800 GB in size. 
	Given its size, \image{} requries $10$ Summit nodes to perform hierarchical clustering.

@@

\begin{figure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_rank2_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synrank2speedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_rank2_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwrank2speedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Rank-2 NMF }
\label{fig:rank2speedup}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_rank2_strongscaling.pdf}
\caption{Time Breakdown for Rank-2 NMF on \image{} }
\label{fig:rwrank2strongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_hierarchical_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synhierspeedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_hierarchical_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwhierspeedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Hierarchical Clustering}
\label{fig:rank2speedup}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering on Synthetic Data}
\label{fig:synhierstrongscaling}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering on \image{}}
\label{fig:rwhierstrongscaling}
\end{center}
\end{figure}
